%% CV — Mahima Prajapati
%% Targeted for: 2026 Summer Additive Manufacturing Intern (BS/MS) — Applied Materials (Gloucester, MA)
%% Compile with: pdflatex main_applied_materials.tex

\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Mahima Prajapati - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.77]{geometry}
\usepackage{import}

% personal data
\name{Mahima}{Prajapati}
\address{Blacksburg, Virginia, USA}{}{}
\email{mahimap@vt.edu}
\extrainfo{\href{https://linkedin.com/in/mahimaprajapati}{LinkedIn}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{PhD candidate in Aerospace Engineering at Virginia Tech with deep expertise in additive manufacturing process simulation and measurement-driven engineering analysis. Research focuses on Abaqus-based FEA modeling of metal AM processes (DED, AFSD) to predict thermo-mechanical deformations and validate against physical manufacturing outcomes. Published AIAA SciTech researcher with experience designing and executing simulation studies, interpreting data, and communicating findings to both technical and non-technical audiences. Brings strong analytical rigor, MATLAB proficiency, and a structured research methodology to support Applied Materials' additive manufacturing team in advancing next-generation component development and process best practices.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Additive Manufacturing Analysis:} Abaqus (expert) --- thermo-mechanical simulation of metal AM processes; measurement and analysis supporting AM component design; process parameter evaluation and quality assessment.
\vspace{1pt}

\item \textbf{Computational Analysis \& Scripting:} MATLAB --- numerical methods, data processing, simulation scripting; quantitative analysis and technical reporting; best-practice documentation.
\vspace{1pt}

\item \textbf{FEA \& Structural Simulation:} Abaqus, ANSYS --- static and dynamic structural analysis, material property evaluation, model validation against experimental data.
\vspace{1pt}

\item \textbf{CAD \& Design:} SolidWorks, CATIA --- mechanical design and assembly for additively manufactured components; design-for-manufacturability considerations.
\vspace{1pt}

\item \textbf{Research Communication:} AIAA-published author; experienced in publishing technical findings and developing internal knowledge resources; instructor to 50+ engineering students; LaTeX documentation.

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{Jan 2025--Present}{Doctor of Philosophy --- Aerospace \& Ocean Engineering}{Virginia Tech}{Blacksburg, VA}{}{\vspace{1pt}
Research: Metal additive manufacturing process simulation; Abaqus FEA of DED and AFSD processes; measurement and validation of thermo-mechanical deformation predictions against physical manufacturing data.
}}

\vspace{3pt}

\item{\cventry{Aug 2021--Dec 2024}{Master of Science --- Aerospace Engineering}{Virginia Tech}{Blacksburg, VA}{}{\vspace{1pt}
Thesis: ``Aeroelastic Analysis of a Uniform Cantilever Wing with Distributed Electric Propulsors with Rotary Inertia.'' Published at AIAA SciTech Forum 2026. \href{https://doi.org/10.2514/6.2026-1649}{DOI: 10.2514/6.2026-1649}
}}

\vspace{3pt}

\item{\cventry{2016--2020}{Bachelor of Engineering --- Mechanical Engineering}{M.H.\ Saboo Siddik College of Engineering}{Mumbai, India}{}{}}

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{Jan 2025--Present}{PhD Researcher --- Metal Additive Manufacturing Simulation}{Virginia Tech, Kevin T. Crofton Dept. of Aerospace \& Ocean Engineering}{Blacksburg, VA}{}{\vspace{1pt}
\begin{itemize}
    \item Developing and validating Abaqus FEA simulations of metal AM processes (DED, AFSD); collecting and analyzing process data to refine model accuracy against physical manufacturing outcomes.
    \vspace{1pt}
    \item Evaluating material properties and thermo-mechanical behavior in simulated AM components; applying findings to improve process parameter selection and part quality.
    \vspace{1pt}
    \item Documenting research findings and best-known methods; preparing manuscripts for AIAA SciTech 2027 and a peer-reviewed journal.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{Aug 2021--Dec 2024}{Graduate Researcher \& Teaching Assistant}{Virginia Tech}{Blacksburg, VA}{}{\vspace{1pt}
\begin{itemize}
    \item Designed and executed systematic aeroelastic simulation studies; published peer-reviewed findings at AIAA SciTech 2026 (\href{https://doi.org/10.2514/6.2026-1649}{DOI: 10.2514/6.2026-1649}).
    \vspace{1pt}
    \item Provided technical guidance and lab instruction to 50+ undergraduate students; developed tutorials and graded technical reports.
    \vspace{1pt}
    \item Awarded \textbf{First Place --- Innovation \& Technology Advancement} at Virginia Tech GPSS (\$275 award) for research poster presentation.
\end{itemize}}}


\end{itemize}

% ============================================================
%     PUBLICATIONS
% ============================================================

\section{Publications}
\vspace{1pt}
\begin{itemize}
\item Prajapati, M.~D., and Kapania, R.~K. (2026). ``Aeroelastic Analysis of a Uniform Cantilever Wing with Distributed Electric Propulsors with Rotary Inertia.'' \textit{AIAA SciTech Forum 2026}. \href{https://doi.org/10.2514/6.2026-1649}{DOI: 10.2514/6.2026-1649}
\item Prajapati, M.~D., and Kapania, R.~K. (2027). ``Effect of Thrust on Aeroelastic Analysis of DEP Wings with Rotary Inertia.'' \textit{AIAA SciTech Forum 2027}. (In preparation; journal paper forthcoming.)
\end{itemize}

% ============================================================
%     HONORS AND AWARDS
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{First Place --- Innovation \& Technology Advancement} -- Virginia Tech Graduate \& Professional Student Symposium (GPSS); \$275 monetary award.}
\item{\textbf{Tolson \& Nerney Fellowship} -- Kevin T. Crofton Dept.\ of Aerospace \& Ocean Engineering, Virginia Tech (2025); \$11,750.}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
